Automated Lensing Learner - I: An automated Strong Lensing Identification Pipeline

### 2017-03-09 ms.tex
Finished text for discussion/summary.  Need to follow-up on what data set I had used where the AUC for nLSST10 was .96, and .86 for LSST10.  Was likely the one with constant zlens????

% Summarize paper
We have presented a supervised classification pipeline to
automatically identify galaxy-galaxy strong lensing systems using a
histogram of oriented gradients as a feature extractor, and logistic
regression as a machine learning algorithm.  Our pipeline can easily
be extended to identify other strong lensing features, such as
multiply imaged quasars, and to test alternative features and/or
machine learning algorithms.

% Training set
We have also made use of a new sophisticated set of mock observations,
which will also be made publicly available.  The lensing systems have
lens galaxies generated with a realistic redshift distribution and
along the line of sight galaxies drawn from ultra-deep Hubble
observations.  We have explored results from mock HST, one year LSST,
and ten year LSST observations.

@@

\item We have tested HOG as an efficient and effective feature
  extractor for galaxy-galaxy strong lensing systems in both a space
  based (HST-like) and ground based (LSST-like) observation.

\item We have found almost no difference between the Logistic
  Regression and Support Vector Machine algorithms, with Logistic
  Regression performing at a factor of $XX$ faster.

\item We find AUC values of ROC curves of optimized classifier models
  to yield $AUC=0.987$ for the HST-like data, $AUC=0.96$ for the
  stacked LSST-like data with the lensing BCG included, and $AUC=0.86$
  for the stacked LSST-like data with the lensing BCG perfectly
  removed.  This suggests that we will be able to use our method to
  detect strong galaxy-galaxy lensing systems in future space-based
  missions (e.g. {\em Euclid}) with high purity and completeness.
  However, for future ground-based missions like LSST, we will need to
  perform additional image pre-processing, such as subtracting the
  image component corresponding to the lens.

\item Images that were easiest for our model to classify typically
  were lens systems that had high magnification and a BCG with large
  velocity dispersion.

\end{itemize}
%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

% Impact of work
These results indicate that...

% Caveat of the mock data set
One major caveat ... training and test mock images... LOS galaxies all
from Hubble Ultra Deep field.  Success measured by performance on the
small sample of systems observed with HST.

% Interpreting TP and FP rates
Note that while our training and test set split of $50\%$ lensed and
$50\%$ unlensed images is not realistic, our true positive and false
positive rates in the ROC curves would stay the same for alternative
lensed and unlensed sample splittings.

On the other hand, the ROC curves show a representative rate for lens
and source distributions that are evenly sampled.  The sampling is
{\it not} representative of what we might expect from a an
observational survey.

>>>>

% Summarize paper
We have presented a supervised classification pipeline to
automatically identify galaxy-galaxy strong lensing systems using a
histogram of oriented gradients (HOG) as a feature extractor, and
logistic regression (LR) as a machine learning algorithm.  Our
pipeline can easily be extended to identify other strong lensing
features, such as multiply imaged quasars, and to test alternative
features and/or machine learning algorithms.

% Training set
We have also made use of a new sophisticated set of mock observations,
which will also be made publicly available.  The lensing systems have
lens galaxies generated with a realistic redshift distribution and
along the line of sight galaxies drawn from Hubble Ultra-Deep field
observations.  We have explored results from mock HST, one year LSST,
and ten year LSST observations.

@@

\item We have tested and run parameter tests for a histogram of
  oriented gradients as an efficient and effective feature extractor
  for galaxy-galaxy strong lensing systems in both a space based
  (HST-like) and ground based (LSST-like) observation.  We have also
  tested and run parameter tests for logistic regression as a
  scalable, cheap, and effective machine learning algorithm.

\item We find AUC values of ROC curves of optimized classifier models
  to yield $AUC=0.975$ for the HST-like data, $AUC=0.809$ for the
  stacked LSST-like data.  Model performance exhibits continual
  increase with the training size.

\item While removal of the lens galaxy improves model performance for
  smaller size training samples, features from the lens galaxy improve
  model performance for larger training data sets.

\item Images that were easiest for our model to classify typically
  were lens systems that had high lensed image magnification and a
  lens galaxy with large velocity dispersion or non-lens systems with
  lens galaxies with smaller velocity dispersion and non-elongated
  along the line of sight galaxies.
\end{itemize}
%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

% Impact of work
These results indicate that effective image classification of
galaxy-galaxy strong lensing systems do not require large scale
computing resources.

% Caveat of the mock data set
One major caveat of our resuls is the fact that our mock data likely
does not describe the full range of lens and non-lens images that will
be observed.  For example, the along the line of sight galaxies in our
training and test images all come from the Hubble Ultra Deep field,
sampling a smaller range of potential systems that are not associated
with a lensed image.  We will address these shortcomings in subsequent
work.

% Interpreting TP and FP rates
Finally, we must take the class balance, or relative number of lens to
non-lens systems, into account when assessing a metric.  The
Purity-Recall (purity-completeness) metric is sensitive to the ratio
of lens and non-lens systems in the data.  Both of our training and
test data sets have $50\%$ lensed and $50\%$ unlensed images, which is
not expected in observations.  The ROC curve metric is insensitive to
the ratio, but is sensitive to the sampling.  Given alternative lens
and non-lens sample splittings, our true positive and false positive
rates in the ROC curves would stay the same, making the ROC curve a
more standard metric in the literature.  On the other hand, the ROC
curves show a representative rate for lens and source distributions
that are evenly sampled.  We do {\it not} expect this sampling to be
representative of what we might expect from a an observational survey.
